Evaluating the Performance and Energy Efficiency of COSMO-ART, a Coupled Numerical Weather Forecast and Chemical Transport Model

### 2014-04-16 paper_enahpc14/Sec4:Evaluation.tex
add minor changes to the bibliography, section 3 & section 4

In  this  section, we  present  a  performance  and energy  efficiency
evaluation  of  different  achitectures  when  running  the  COSMO-ART
baseline.  We  start by  specifying our measurement  methodology along
with the metrics used to  analyse the results on all platforms.  Then,
we detail the environment  setup gathering the considered HPC systems,
the software  environment and the runtime  configuration.  Finally, we
discuss  benchmark   results  and  power-performance   traces  of  the
application.

\subsection{Measurement methodology}
\label{subsec:4.1}
We  approach  the  assessment  of  the energy  footprint  and  overall
performance    of    COSMO-ART    with    two    important    metrics:
\textit{time-to-solution}       and       \textit{energy-to-solution}.
Time-to-Solution  refers   to  the  total  wall  clock   time  of  the
application execution time. Energy-to-solution is the amount of energy
spent  to achieve  results.  Energy  consumption of  CSCS  clusters is
assessed  by sampling  the instantaneous  peak power  during execution
which  is then  averaged  and multiplied  by  the time-to-solution  to
determine energy-to-solution.   Whenever possible, multiple production
runs of COSMO-ART were  performed to illustrate the reproducibility of
the baseline, and quantify  the significant uncertainties in the power
measurement, as dictated by the available technology.

@@

\subsubsection{Tintorrum (UJI)}
Tintorrum, which is installed at the Jaume I University (UJI),  is an 
heterogeneous cluster composed of 28 compute nodes. For our experiments
only a subset of these nodes were considered. This set is composed of 
16 nodes, each of which includes two Intel Xeon E5645 hexa-core processors at 
2.40 GHz connected via Infiniband QDR (Mellanox MTS3600 switch). 
Each core has 32 KB instruction and 32 KB data L1 caches and 
256 KB L2 cache. The 6 cores share a 12 MB L3 cache and the platform has 
288 GB of DDR3 1333 MHz.

>>>>

In  this section,  we  describe a  performance  and energy  efficiency
evaluation  of  different  achitectures  when  running  the  COSMO-ART
baseline.  We  start by  specifying our measurement  methodology along
with the metrics used to  analyse the results on all platforms.  Then,
we detail the environment  setup gathering the considered HPC systems,
the  software  environment and  the  run  configuration.  Finally,  we
discuss benchmark  results and  power-performance traces of  the model
system.

\subsection{Measurement methodology}
\label{subsec:4.1}
We  approach  the  assessment  of  the energy  footprint  and  overall
performance    of    COSMO-ART    with    two    important    metrics:
\textit{time-to-solution}       and       \textit{energy-to-solution}.
Time-to-solution  refers   to  the  total  wall  clock   time  of  the
application execution time. Energy-to-solution is the amount of energy
spent  to achieve  results.  Energy  consumption of  CSCS  clusters is
assessed  by sampling  the instantaneous  peak power  during execution
which  is then  averaged  and multiplied  by  the time-to-solution  to
determine energy-to-solution.   Whenever possible, multiple production
runs of COSMO-ART were  performed to illustrate the reproducibility of
the baseline, and quantify  the significant uncertainties in the power
measurement, as dictated by the available technology.

@@

\subsubsection{Tintorrum (UJI)}
Tintorrum, which  is installed at the  Jaume I University  (UJI), is a
heterogeneous  cluster   composed  of  28  compute   nodes.   For  our
experiments only a subset of  these nodes were considered. This set is
composed  of 16 nodes,  each of  which includes  two Intel  Xeon E5645
hexa-core  processors  at  2.40   GHz  connected  via  Infiniband  QDR
(Mellanox MTS3600 switch).  Each core  has 32 KB instruction and 32 KB
data L1 caches and 256 KB L2 cache. The 6 cores share a 12 MB L3 cache
and the platform has 288 GB of DDR3 1333 MHz.
